Holomorphic field theories and higher algebra

### 2024-09-17 draft.tex
quick prune of old stuff

\subsection{An extended aside on perturbative quantization}

\owen{I suggest we mostly move this to a later section and expand it substantially.}

@@

\begin{thm}[Wang, \owen{precise citations}]
For every graph~$\gamma$,
this family has a natural smooth extension to the Schwinger space~$\Schw(\gamma)$.
\end{thm}

>>>>

@@

\begin{thm}[Wang, \owen{precise citations}]
For every graph~$\gamma$,
this family $w_{\gamma,t}$ has a natural smooth extension to the Schwinger space~$\Schw(\gamma)$.
That is, there is a smooth map
\[
w_{\gamma}: \Schw(\gamma) \to \Hom_{cts}(\cV_c^{L(\gamma)},\CC)
\]
where $w_{\gamma,t}$ is a continuous linear functional on $\cV_c^{L(\gamma)}$ for every point $t \in \Schw(\gamma)$.
\end{thm}
